%$Id: cv.tex,v 1.230 2024/12/23 14:54:06 brandenb Exp $
%\documentstyle[11pt]{article}
\documentclass{article}
\usepackage{html,url,color}
\setlength{\oddsidemargin}{+3mm}
\setlength{\textwidth}{160mm}
\setlength{\textheight}{232mm}
\setlength{\topmargin}{-14mm}
%
\input{tex/journals}
\newcommand{\km}{\,{\rm km}}

\date{}
%\title{\bf Curriculum vitae and list of publications}
\title{\bf Curriculum vitae}
\author{Axel Brandenburg\\
\small\today\normalsize}\begin{document}
%\maketitle
%\noindent\LARGE{\bf Appendix B. Curriculum vitae and list of publications of Axel Brandenburg}\normalsize\\
%\noindent\LARGE{\bf Curriculum vitae and list of publications \\ of Axel Brandenburg}\normalsize\\
\noindent\LARGE{\bf Curriculum vitae of Axel Brandenburg}\normalsize\\
%\small December 2, 1994\normalsize}\begin{document}\maketitle
\small \today \normalsize
\\

\noindent
Born: 7 April 1959 in Heide, Federal Republic of Germany\\
Nationality: German\\
Marital status: married, 1 child\\
%henkilotunnus on 070459 209P
%dansk person nummer 070459 3015
\vspace{-4mm}

\section*{Address}
% 
%Observatory and Astrophysics Laboratory, University of Helsinki\\
%T\"ahtitorninm\"aki, SF-00130 Helsinki, Finland \\
%Telephone: + 358 - 0 - 191 2948\\
%e-mail: brandenburg@csc.fi
% 
%NORDITA, Blegdamsvej 17, DK 2100 Copenhagen \O, Denmark\\
%Telephone: + 45 - 353 25 228 \\
%FAX: + 45 - 353 89 157 \\
%e-mail: {\sf brandenb@nordita.dk}\\
%\url{http://www.nordita.dk/~brandenb}
% 
%Issac Newton Institute, 20 Clarkson Road, Cambridge CB3 0EH, UK\\
%Telephone: + 44 - 223 33 0555\\
%FAX: + 44 - 223 33 0508\\
%e-mail: brandenb@newton.cam.ac.uk\\
% 
%HAO/NCAR, P.O. Box 3000, Boulder, CO 80307-3000, USA\\
%FAX + 1 (303) 497 1589, Tel + 1 (303) 497 1586\\
%e-mail: brandenb@hao.ucar.edu\\
%School of Mathematics and Statistics\\
%Department of Mathematics\\
%University of Newcastle\\
%Newcastle upon Tyne, NE1 7RU, UK\\
%Tel: +44 191 222-7312\\
%FAX: +44 191 222-8020\\
%email: Axel.Brandenburg@Newcastle.ac.uk\\
%http://antares.ncl.ac.uk/~brandenb
%

% Laboratory for Atmospheric and Space Physics,
% Department of Astrophysical and Planetary Sciences, \& JILA,
% University of Colorado, 3665 Discovery Drive, Boulder, CO 80303, USA\\
% %Axel.Brandenburg@Colorado.edu, phones: (303) 492-9309 and (303) 735-7738\\
% {\sf Axel.Brandenburg@Colorado.edu}, phone: (303) 735-7738\\

\vspace{-2mm}\noindent
Nordita, KTH Royal Institute of Technology and Stockholm University,
AlbaNova University Center,
Hannes Alfv\'ens v\"ag 12, SE - 106 91 Stockholm, Sweden;
%Telephone: +46 8 5537 8707, \quad FAX: +46 8 5537 8404, \quad mobile: +46 7 3270 4376 \\
%\vspace{-2mm}\noindent
e-mail: {\sf brandenb@nordita.org},\\
\quad\url{http://www.nordita.org/~brandenb},
\quad\url{http://orcid.org/0000-0002-7304-021X}

\section*{Education}
%
\begin{description}\itemsep-1mm

\item Docent of Astronomy, University of Helsinki, March 1992

\item Dr. Phil., University of Helsinki, May 1990,
Doctoral dissertation: {\em Challenges for solar dynamo theory: 
$\alpha$-effect, differential rotation and stability},
ISBN 952-90-1697-2
%, ``magna cum laude approbatur''

\item Lic. Phil., University of Helsinki, February 1989,
Licentiate thesis: {\em Kinematic dynamo theory and the solar activity cycle}
%, ``eximia cum laude approbatur''

\item Dipl. Phys., University of Hamburg, January 1986,
Diploma thesis: {\em Hydrodynamics of convective bubbles 
in linear approximation}
%, ``sehr gut''

%\item Abitur, Werner Heisenberg Gymnasium, Heide, June 1978

\end{description}
 
\section*{Employment}
% 
\begin{tabbing}
Jan 2007 -- present:\quad\quad \=Professor of Astrophysics, Stockholm Observatory, NORDITA, Stockholm\\
%May 2018 -- present:\>Adjunct Professor, Carnegie Mellon University \\
Aug 2015 -- Jul. 2018:\>Visiting Faculty, University of Colorado, Boulder (LASP, APS, and JILA)\\
Jan 2000 -- Dec. 2006:\>Professor of Astrophysics, NORDITA, Copenhagen\\
Feb 1996 -- Dec. 2000:\>Professor of Applied Mathematics, University of Newcastle upon Tyne\\
Dec 1994 -- Jan. 1996:\>Nordic Assistant Professor, Nordita, Copenhagen\\
Dec 1992 -- Nov. 1994:\>Postdoctoral Research Fellow, High Altitude Observatory/NCAR, Boulder\\
% SERC Grant GR G59981
%Mar 1992            \>Docent of Astronomy, University of Helsinki\\
Aug 1992 -- Nov. 1992:\>Visiting Fellowship, University of Cambridge\\
Sep 1990 -- Aug. 1992:\>Postdoctoral Research Fellow, Nordita, Copenhagen\\
\end{tabbing}

\section*{Publications}
Below the numbers of publications (published or in print)
and the $h$ indexes (from Web of science, ResearcherID: I-6668-2013),
the Astrophysical Data Service (ADS), and Google Scholar (GS); see also:\\
\url{http://www.nordita.org/~brandenb/pub/node1.html}\\
\\
Number of papers in refereed journals: 459 + 5 submitted\\
Number of invited conference reviews: 43\\
Number of communications to scientific meetings: 86\\
Total number of citations:
% Hamburg or Helsinki or Newcastle or boulder or stockholm or copenhagen
17069, $h$-index 65 (on Web of Science); %WoS (3-jun-23)
20784, $h$-index 70 (ADS); and \\ %(25-Jan-23)
27505, $h$-index: 84 (on Google Scholar)\\ %(12-nov-24)

\section*{Influential papers}

{\it
The second column refers to the paper number in the full list of publications,\\
%\url{http://www.nordita.org/~brandenb/pub/node1.html}}\\
\url{http://norlx65.nordita.org/~brandenb/pub/node1.html}}\\
%Citations are from Web of Science (WoS$^*$),
Citations are from Web of Science (WoS),
Astrophysical Data Service (ADS), and Google Scholar (GS).\\
%$^*$not up-to-date
\vspace{2mm}

\begin{tabular}{llrrr}
      &    & \multicolumn{3}{c}{citations}\\
%paper:& $\;\;$\# & WoS$^*$ & ADS & GS \\
paper:& $\;\;$\# & WoS & ADS & GS~ \\
\hline        
Brandenburg \& Subramanian (2005)              & A.153 &1186 &1381 &1895 \\
Beck, Brandenburg et al.\ (1996)               & A.58  & 801 & 883 &1267 \\
Brandenburg et al.\ (1995)                     & A.44  & 698 & 760 &1095 \\
Brandenburg (2001)                             & A.98  & 439 & 486 & 685 \\
Brandenburg (2005)                             & A.145 & 354 & 341 & 438 \\
Haugen, Brandenburg, \& Dobler (2004)          & A.133 & 269 & 302 & 401 \\
Saar \& Brandenburg (1999)                     & A.90  & 257 & 288 & 381 \\
Brandenburg, Enqvist, \& Olesen (1996)         & A.54  & 231 & 276 & 349 \\
Nordlund, Brandenburg, et al.\ (1992)          & A.22  & 217 & 230 & 299 \\
Brandenburg \& Dobler (2002)                   & A.111 & 194 & 214 & 299 \\
Brandenburg et al.\ (1996)                     & A.52  & 192 & 202 & 291 \\
Dobler, Stix, \& Brandenburg (2006)            & A.159 & 177 & 203 & 289 \\
Christensson, Hindmarsh, \& Brandenburg (2001) & A.104 & 172 & 197 & 247 \\
Brandenburg et al.\ (1989)                     & A.3   & 174 & 184 & 232 \\
Korpi, Brandenburg, et al.\ (1999)             & A.82  & 164 & 180 & 238 \\
Blackman \& Brandenburg (2002)                 & A.115 & 146 & 167 & 213 \\
R\"udiger \& Brandenburg (1995)                & A.41  & 146 & 149 & 199 \\
%Pudritz et al.\ (2007)                & B.25  & --- & 301 & 209 \\
\end{tabular}
\vspace{2mm}

\section*{PhD students}

\begin{tabbing}
Stephen J. Brooks: ~\= 1996--2000\quad \= (Newcastle upon Tyne)\\
Alberto Bigazzi:    \> 1996--2000  \> (Newcastle upon Tyne and L'Aquila, Rome)\\
Maarit J.\ Korpi:   \> 1997--1999  \> (Oulu U)\\
Nils E.\ L. Haugen  \> 2000--2004  \> (Trondheim, NTNU)\\
Tarek A. Yousef     \> 2000--2004  \> (Trondheim, NTNU)\\
Antony J. Mee       \> 2002--2006  \> (Newcastle upon Tyne, co-supervisor)\\
Simon Candelaresi   \> 2009--2012  \> (Stockholm U, Phil. Lic. in Feb. 2011)\\
Fabio Del Sordo     \> 2009--2012  \> (Stockholm U, Phil. Lic. in Feb. 2011)\\
Koen Kemel          \> 2009--2012  \> (Stockholm U, Phil. Lic. in Aug 2011)\\
J\"orn Warnecke     \> 2009--2013  \> (Stockholm U, Phil. Lic. in May 2011)\\
Sarah Jabbari       \> 2012--2016  \> (Stockholm U, Phil. Lic. in May 2014) \\
Illa R. Losada      \> 2013--2019  \> (Stockholm U, Phil. Lic. in Dec 2014) \\
Xiang-Yu Li         \> 2014--2018  \> (Stockholm U, Phil. Lic. in May 2016) \\
Alberto Roper Pol   \> 2017--2020  \> (University of Colorado) \\
Yutong He           \> 2020--2204  \> (Stockholm U, Phil. Lic. in Dec 2022) \\
\end{tabbing}
\vspace{-4mm}

\noindent
Master students: Atefeh Barekat (2013), Nousaba Nasrin Protiti (2023)

\vspace{4mm}
\noindent
Batchelor students: Julia Asplund (2019), Gustav Larsson (2023)

%\begin{itemize}\itemsep -2pt
%\item
%University of Helsinki: Maarit J.\ Korpi$^*$ (1999)
%\item
%University of Newcastle: Stephen J.\ Brooks$^*$ (2000), Antony J.\ Mee (2006)
%\item
%University of L'Aquila: Alberto Bigazzi (2000)
%\item
%University of Trondheim: Nils E.\ L.\ Haugen (2004), Tarek A.\ Yousef (2004)
%\item
%Stockholm University: Simon Candelaresi$^*$, Fabio Del Sordo$^*$,
%Koen Kemel$^*$ (2012), J\"orn Warnecke$^*$ (2013),
%Sarah Jabbari$^*$ (2016$^{**}$), Illa R.\ Losada$^*$ (2016$^{**}$)
%\end{itemize}
%\vspace{-4mm}
%$^*$ I was the official supervisor, $^{**}$ anticipated defense date.
%\vspace{4mm}

%\section*{Licentiate theses}

%\begin{tabbing}
%Simon Candelaresi   \> 2011  \> (Stockholm U)
%Fabio Del Sordo     \> 2011  \> (Stockholm U)
%\end{tabbing}

%\noindent {\em (iii) Supervised post-doctoral fellows}
%\begin{itemize}\itemsep -2pt
%\item
%Marie Curie Fellows: F.J. Sanchez-Salcedo (1999), Boris Dintrans (2001)
%\item
%Project grants: Brigitta von Rekowski (2001), Anne Bardou (2001),
%Wolfgang Dobler (2001),
%Alexander Hubbard (2011), Piyali Chatterjee (2011), Gustavo Guerrero (2011)
%\item
%Nordita fellows in astrophysics: 15 since 2001
%%Anja Andersen, Mattias Christensen, Raphael Plasson, Maarit Korpi,
%%Petri Kapyla, Oleg Kochukhov, Karen Guldbaek, Ebru Devlen,
%%Van Eysden, Oliver Gressel, Mikhail Modestov, Chi-kwan Chan,
%%Niccolo Bucciantini, Eniko Madarassy, Torgny Karlsson
%\end{itemize}

\section*{Teaching experience}

\begin{itemize}

\item[--] {\it Advanced Astrophysical Fluid Dynamics}
(7.5 ECTS) at Stockholm U, postgraduate level (2021)

\item[--] {\it Search for Life in the Universe}
(44 hours) at CU-Boulder, for non-science majors (2017, spring+fall)

\item[--] {\it Fluid Instabilities, Waves, \& Turbulence}
(44 hours) at CU-Boulder, graduate level (2016)

\item[--] {\it Solar \& Space Physics}
(44 hours) at CU-Boulder, upper undergraduate level (2016)

\item[--] {\it Astrophysical Fluid Dynamics}
(7.5 ECTS) at Stockholm U, postgraduate level (2013)

\item[--] {\it Astrophysical Magnetohydrodynamics}
(7.5 ECTS) at Stockholm U, master level (2012)

\item[--] {\it Solar Physics and Magnetohydrodynamics}
(7.5 ECTS) at Stockholm U, postgraduate level (2009)

\item[--] {\it Pencil Code tutorials},
taught in Trieste (Italy, 2009) and Aussois (France, 2009)

\item[--] {\it Solar Physics}
(12 hours) at the IRF Kiruna (2005, 2006, 2007, 2008), postgraduate level

\item[--] {\it Planetary and Stellar Orbits}
(24 hours) at University of Newcastle upon Tyne (1998, 1999, 2000),
second year students

\item[--] {\it Introduction to Astrophysical Fluids}
(24 hours) at University of Newcastle upon Tyne (1997, 1998, 1999),
second year students

\item[--] {\it Fluid Flow and Cosmic Fluids}
(24 hours) at University of Newcastle upon Tyne (1997, 1998, 1999),
third year students

\item[--] {\it Relativistic Fluid Dynamics and Visualization}
(24 hours) at Copenhagen University (1995/1996), shared with {\AA}ke Nordlund,
postgraduate level

\end{itemize}

\section*{Notable recognitions}

\begin{itemize}\itemsep-1pt
\item[2014]
Elected foreign member of the Royal Swedish Academy of Sciences\\
\url{https://www.kva.se/en/news/ny-ledamot-invald-i-akademien-2-3/}

\item[2019]
Honorary professor of Ilia State University (Tbilisi/Georgia)

\item[2019]
Distinguished Fellow of NYUAD (Abu Dhabi)

\item[2022]
Jes\'us Serra Foundation visiting fellow at the Institute of Astrophysics of the Canary Islands

\end{itemize}

\section*{Major grants}

\begin{itemize}

\item
VR project grant, ``Stochastic Gravitational Wave Background from the Early Turbulent Universe''
2019-04234, January 2020 -- December 2022, 4.00 MSEK (430 k\$, as PI)

\item
NSF Astronomy and Astrophysics Research Grants (AAG),
``Collaborative research: A Comprehensive Theoretical Study of Cosmic
Magnetic Fields their Origin, Evolution, and Signatures''
1615100, July 2016 -- June 2019, 224 k\$ (as Co-I/Institutional PI;
PI: Tina Kahniashvili, Carnegie Mellon University)
%13008907

\item
Knut \& Alice Wallenberg Foundation,
``Bottlenecks for the growth of particles suspended in turbulent flows''
January 2015 -- December 2019, 44 MSEK (4.67 M\$, as Co-I)

\item
Research Council of Norway (RCN), FRINATEK research grant
``Particle transport and clustering in turbulent flows''
231444, July 2014 -- June 2017, 7.25 MNOK
(1.18 M\$, as PI)
% http://www.nordita.org/~brandenb/TurboPart/

\item
VR breakthrough research grant, ``Formation of active regions in the Sun''
2012-5797, January 2013 -- December 2016, 4.2 MSEK
(0.63 M\$, as PI)

\item
VR project grant, ``Turbulent dynamo simulation in a spherical shell segment''
621-2011-5076, January 2012 -- December 2014, 1.65 MSEK
(0.25 M\$, as PI)

\item
ERC Advanced Grant, ``Astrophysical Dynamos'' No 227952,\\
February 2009 -- January 2014, 2.22 MEuro
(2.8 M\$, as PI)
% 2009, 10, 11, 12, 13, Jan 14
% 19,600 SEK
% http://www.nordita.org/~brandenb/AstroDyn/

\item
PPARC Research Grant, ``Accretion Discs and Jets'' PPA/G/S/1997/00284,\\
1998 -- 2001, 270 kGBP
(0.42 M\$, as PI)

\end{itemize}

\section*{Fields of research}

%Solar physics, 
Astrophysical fluid dynamics, 
with emphasis on dynamo and turbulence theories;
astrobiology, with emphasis on homochirality.
Particular interests: solar and stellar activity, helioseismology,
convection, differential rotation, galactic turbulence and magnetism,
accretion discs, fractals in turbulence, relativistic hydrodynamics,
early universe, relic gravitational waves, magnetospheric physics.
\\

\section*{Organization of conferences and programs}

\begin{tabbing}
Jan~\= 2024 ~~\= Program on Turbulence in Astrophysical Environments (KITP, Santa Barbara) \\
Aug~\= 2022 ~~\= Program on Magnetic field evolution in low density or strongly stratified plasmas (Stockholm) \\
Aug~\= 2019 ~~\= Program on Gravitational Waves from the Early-Universe (Stockholm) \\
Jun~\= 2018 ~~\= 14th Pencil Code User Meeting (Boulder) \\
Jun~\= 2015 ~~\= Program on Origin, Evolution, and Signatures of Cosmological Magnetic Fields (Stockholm)\\
Oct~\= 2012 ~~\= 12th European Workshop on Astrobiology (Stockholm)\\
Aug~\= 2011 ~~\= Program on Dynamo, Dynamical Systems and Topology (Stockholm)\\
May~\= 2011   \> Program on Predictability + School on Data Assimilation (Stockholm) \\
Feb~\= 2011   \> R\"adlerFest: $\alpha$ effect and beyond (Stockholm) \\
May~\= 2010   \> Program on Turbulent combustion (Stockholm) \\
Sep~\= 2009   \> Program on Solar and Stellar Cycles (Stockholm) \\
Mar~\= 2008   \> Program on Turbulence and Dynamos (Stockholm) \\
Feb~\> 2008   \> Program on the Origins of Homochirality (Stockholm) \\
Nov~\> 2007   \> Joint Nordic and SwAN Astrobiology meeting (Stockholm) \\
Aug~\> 2007   \> 3rd Pencil Code User Meeting (Stockholm) \\
May~\> 2007   \> New Trends in Radiation Hydrodynamics (Stockholm) \\
Jan~\> 2006   \> NorFA Winter School on Astrobiology (Levitunturi, Finnish Lapland)\\
Jul~\> 2005   \> Nordita Master Class in Physics (Hiller\o d)\\
Jan~\> 2005   \> Astrobiology and Origins of Life (Copenhagen)\\
Jan~\> 2005   \> Meeting on Nordic Science Outreach (Copenhagen)\\
Sep~\> 2004   \> Cosmic Ray Dynamics: from Turbulent to Galactic Scale Magnetic Fields (Copenhagen)\\
Aug~\> 2004   \> Astrobiological Problems for Physicists and Biologists (Turku, Finland)\\
Jan~\> 2004   \> Astrobiological Problems for Physicists (Copenhagen)\\
Jul~\> 2002   \> Nordita Master Class in Physics (Hiller\o d)\\
Jul~\> 2001   \> Nordita Master Class in Physics (Hiller\o d)\\
Mar~\> 2001   \> Dynamos in the Laboratory, Computer, and the Sky (Copenhagen)\\
Jul~\> 2000   \> Nordita Master Class in Physics (Copenhagen)\\
Jan~\> 2000   \> Physics of Accretion and Associated Outflows (Copenhagen)\\
May~\> 1997   \> UK-MHD meeting (Newcastle, England)\\
Feb~\> 1996   \> NorFA Winter School on Magnetic fields in Space and Astrophysics (Levitunturi, Finnish Lapland)\\
\end{tabbing}
\vspace{-8mm}
 
\section*{Invited participation in research programs}

\begin{tabbing}
Nov~\= 2022 ~~\= Frontiers in dynamo theory: from the Earth to the stars, 3 weeks (Cambridge) \\
Jun~\> 2019 ~~\> Turbulent Life of Cosmic Baryons, 3 weeks (Aspen) \\
Feb~\> 2011 ~~\> Turbulence Theory, 1 month (Santa Barbara) \\
Jun~\> 2008 ~~\> Dynamo Theory, 1.5 month (Santa Barbara) \\
Nov~\> 2007 ~~\> Star Formation through Cosmic Time, 1 month (Santa Barbara) \\
Sep~\> 2004 ~~\> Magnetohydrodynamics of Stellar Interiors, 3 months (Cambridge) \\
Jun~\> 2002 ~~\> Dynamo Theory, 3 weeks (Aspen) \\
Jan~\> 2002 ~~\> Solar Magnetism and Related Astrophysics, 3 months (Santa Barbara) \\
Apr~\> 2000 ~~\> Astrophysical Turbulence, 3 months (Santa Barbara) \\
Jan~\> 1998 ~~\> Dynamics of Astrophysical Discs, 3 months (Cambridge) \\
Aug~\> 1992 ~~\> Dynamo Theory, 3 months (Cambridge) \\
\end{tabbing}
\vspace{-8mm}

%Thesis examinations
% Vanhanen 1997 Oulu
% Kerr's college's student, Imperial College London
% Campbell's student 1997 Newcastle
% Paul Dellar, 1998 Cambridge (DAMTP)
% Bertil Dorch 1998 Copenhagen
% Erik Aurell's student, 2001 Stockholm
% XXX Copenhagen (2002)
% Hamburg guy, Potsdam (2000)
% Earth dynamo Potsdam (2007)
% Luis Borgonovo, Gamma rays bursts, 2007 Stockholm
% xxx, Oct 2007 Helsinki
% Luca Naso, 2009 Trieste
% Bidya Karak, 2012, Bangalore
% Nishant Singh, 2012, Bangalore
% ??, 2013 Cape Town, South Africa
% Maire (Linkmann), 2018 Glasgow, UK

%\section*{Scholarships}

%Cultural Foundation of Finland, 1988, 1990\\ 
%Deutscher Akademischer Austauschdienst, 1986-1987\\ 
%Finnish ministry of education, 1986-1987\\ 
%Heikki \& Hilma Honkanen Foundation, 1989\\ 
%Societas Scientiarum Fennica (Magnus Ehrnrooth), 1988, 1990\\ 
%Vilho, Yrj\"o \& Kalle V\"ais\"al\"a stipendium, 1988, 1989\\ 

%Cultural Foundation of Finland, 1990\\ 
%Societas Scientiarum Fennica (Magnus Ehrnrooth), 1990\\ 
%Heikki \& Hilma Honkanen Foundation, 1989\\ 
%Vilho, Yrj\"o \& Kalle V\"ais\"al\"a stipendium, 1989\\ 
%Cultural Foundation of Finland, 1988\\ 
%Societas Scientiarum Fennica (Magnus Ehrnrooth), 1988\\ 
%Vilho, Yrj\"o \& Kalle V\"ais\"al\"a stipendium, 1988\\ 
%Finnish ministry of education, 1986-1987\\ 
%Deutscher Akademischer Austauschdienst, 1986-1987\\ 

\section*{Memberships}

Finnish Physical Society (since 1988) \\
International Astronomical Union (since 1990) \\
American Physical Society (since 1996) \\
European Astrobiology Network Association (since 2005) \\
European Physical Society (since 2011) \\
Member of the Royal Swedish Academy of Sciences (Astronomy and Space Science, 2014)\\

\section*{Other academic activities}

I am frequently consulted as a referee for the following journals:
Astrophysical Journal, Astronomy \& Astrophysics, Geophysical and
Astrophysical Fluid Dynamics, Journal of Fluid Mechanics,
Monthly Notices of the Royal Astronomical Society,
Physical Review (PRL, PRD, and PRE), Physics of Plasmas,
Journal of Computational Physics,
Journal of Cosmology \& Astroparticle Physics,
New Journal of Physics.
On the average my load on reviewing papers is 3 per month.

I am also regularly asked to review research proposals
(NSF, PPARC, DFG, SA, ERC, NRC, VR, Hong Kong, Portugal, Austria)
and to examine PhD theses (Finland, Sweden, Denmark, England, Germany,
France, India, South Africa, USA).
I have been an external panel member for the selection of post-docs
(Finnish Academy; suomen akatemia, SA),
major research grants (Deutsche Forschungsgesellschaft, DFG),
and observing time (European Southern Observatories, ESO).

%As external examiner on PhD theses
%1996 Harri Vanhala (Astronomy, Oulu/Finland) Lic
%1997 Bertil Dorch (Astronomy, Copenhagen/Denmark)
%1998 Paul J. Dellar (DAMTP, Cambridge/UK)
%1998 M. Heritage (Imperial Coll., London/UK)
%2001 Katia Ferriere (Observatoy, Toulouse/France) Habil
%2007 Tiera Laitinen (Finn. Met. Inst., Helsinki/Finland)
%2008 Lisa Rosenqvist (Space Phys., Uppsala/Sweden)
%2014 Daniel Carrera (Astronomy, Lund/Sweden) Lic
%2018 Sofie Liljegren (Astronomy, Uppsala/Sweden)
%2020 Lavail (Kochukov student)(Astronomy, Uppsala/Sweden)

\section*{Administrative experience}

\begin{tabbing}
2021--present ~~\= Deputy director of Nordita \\
2010--present ~~\> Editorial Board Member of Astron. Nachr.\\
2010--2015      \> Deputy director of Nordita \\
2008--2015      \> Chairman of the Swedish Astrobiology Network \\
2007--2009      \> Member of the AlbaNova/Nordita colloquium committee\\
2001            \> Director of the Helmholtz Summer School, Potsdam \\
2000--2002      \> Director of the Nordita Master Class\\
\end{tabbing}
\vspace{-8mm}

\section*{Other merits}

Together with Wolfgang Dobler, I initiated the {\sc Pencil Code} in 2001
as a public domain program for solving partial differential equations
on massively parallel supercomputers.
During 2008--2015 it was hosted through the subversion repository on
Google Code (http://pencil-code.googlecode.com), and
since 2015 it is hosted through \url{https://github.com/pencil-code}.
It has been used for currently over 600 scientific publications; see Ref.D.5
in my full list of publications.

\section*{Public Outreach Experience}

\begin{tabbing}
2019 ~~\= Efter big bang: produktionen av gravitationsv{\aa}gor\\
       \> (Guest lecture at on Oct.\ 31, ABF-huset, Sveav\"agen 41, Stockholm)\\
%2016 ~~\= Guided tours through the Laboratory for Atmospheric and Space Sciences\\
2014 ~~\= Article in Fysikaktuellt: S\"okandet efter en ny teori f\"or solfl\"ackar\\
2010 ~~\= Interview ``Cycles of the Sun'' (British Publishers)\\
       \> (\url{http://www.nordita.org/~brandenb/Solar_Activity_10.pdf})\\
2008   \> Podcast {\it Is All Life Left-Handed?}\\
       \> (\url{http://www.astrobio.net/amee/summer_2008/Radio/radio.php})\\
2005   \> Organizer of Meeting on Nordic Science Outreach (Copenhagen) \\
%http://www.nordita.dk/conference/Outreach05/
2005   \> Co-authored outreach articles with Anja Andersen (Kvant and BioZoom)\\
1990   \> Extended interview in Finnish Television (Prisma program, YLE)\\
\end{tabbing}
\vspace{-8mm}

\section*{Language skills}

\noindent
Native: German\\
Fluent: English and Finnish\\
Basic knowledge: Swedish\\

\section*{Hobbies}

Cycling, hiking, swimming.
Participated in the $3\km$ Vansbrosimningen
(\url{https://en.wikipedia.org/wiki/Vansbrosimningen})
% in 2024 and swam the $3\,$km in 1 hour and 10 minutes; see
%(\url{https://results.vansbrosimningen.se/search/414154})
%(start number 8361).
%The average across all ages is 1 hour and 12--18 minutes,
%depending on the variant.
and the $5\km$ G\"ota Kanalsimmet (\url{https://www.gotakanalsimmet.se/}).
%in 2024 and swam the $5\,$km in 2 hours and 20 minutes; see
%\url{https://my4.raceresult.com/296883/RRPublish/data/pdf?name=Online%7CFinal&contest=0&lang=en}.

\vspace{8mm}
%\newpage

\section*{Publications}
\input{tex/publications}
%\input meetings_short.tex
\end{document}
